The first high-redshift changing-look quasars

### 2020-07-10 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
BH_VirialMasses.py looking good...

This approach assumes that the broad-line region (BLR) is virialized
\citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
Mejia-Restrepo2018}.  {\bf However, the \civ\ line is observed to have
line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
strong blueshifts \citep[as mentioned in the Introduction, see
][]{Richards2011}, and a component of the line profile that does not
reverberate \citep[][]{Denney2012}.  These issues make the virial BH
mass estimate uncertain. \citet{Runnoe2013}, 
\citet{Mejia-Restrepo2016}, \citet{Coatman2017}, 
\citet{Mejia-Restrepo2018} and \citet{Grier2019} all present studies
into improving \civ-based single-epoch black hole mass estimates. With
these cavaets in mind, we acknowledge the BH mass estimates will have
a large error, likely $\sim$0.5 dex. }
The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
  \label{eqn:virial_masses}
\end{equation}
\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

@@

@@

%%
%%  These values are generated using the 
%%
\begin{table}
  \centering
  \begin{tabular}{l l  cc         r}
    \hline
    \hline
                      &                  &                                      &                              & \\
Object            & MJD           &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)  &  $\eta_{\rm Edd}$  \\
                      &                  &                                      &                              & \\
    \hline
                      & $^{\dagger }$53498  &  9.49              &  47.22                  &  -0.378   \\
                      & 53498                      &    9.39            &                    &  $-$0.61   \\
 J1205+3422 & 58538                       &    9.78           &                      &   $-$1.76 \\  
                     & 58693                         &    9.38          &                   &  $-$1.26  \\                    
    \hline
                     & $^{\dagger }$54553    &  8.74            &  46.17   & $-$0.677  \\
                     & 54553                         &   8.84                 &             & $-$1.03  \\
J1638+2827  & $^{\ddagger }$55832  &    9.13                  & 45.98   & $-$1.21  \\      
                      & 55832                        &   8.80                  & 45.98   & $-$1.21  \\     
                      & 58583                        &   9.01                  & 46.50   & $-$0.69   \\
    \hline
                         & $^{\ddagger }$56189   & 8.73                  & 46.23  &  $-$1.24 \\
                         & 56189                         & 8.70                  & 46.23  &  $-$1.24 \\
J2228+2201     & 56960                          &  9.39               & 47.34  & $-$0.12  \\      
                         & 58693                         &  8.97               & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
    We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

>>>>

The continuum
luminosity provides a proxy for the BLR radius, and the broad-line
width (FWHM) provides a proxy for the virial velocity.  This ``virial
mass'' estimate is then expressed as:
{\bf
\begin{equation}
%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
  \label{eqn:virial_masses}
\end{equation}
where $L_{1450}$ is the monochromatic (continuum) luminosity at 1450\AA\,
and FWHM is the full width at half-maximum of the broad \civ\ emission line.
The coefficient $\gamma$ and offset $a$ are generally deteremined empirically.

This approach assumes that the broad-line region (BLR) is virialized
\citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
Mejia-Restrepo2018}.  {\bf However, the \civ\ line is observed to have
line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
strong blueshifts \citep[as mentioned in the Introduction, see
][]{Richards2011}, and a component of the line profile that does not
reverberate \citep[][]{Denney2012}.  These issues make the virial BH
mass estimate uncertain. \citet{Runnoe2013}, 
\citet{Mejia-Restrepo2016}, \citet{Coatman2017}, 
\citet{Mejia-Restrepo2018} and \citet{Grier2019} all present studies
into improving \civ-based single-epoch black hole mass estimates. With
these cavaets in mind, we acknowledge the BH mass estimates will have
a large error, likely $\sim$0.5 dex. }

@@

\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

@@

%%
%%  These values are generated using the 
%%
\begin{table}
  \centering
  \begin{tabular}{l l  cc         r}
    \hline
    \hline
                      &                  &                                      &                              & \\
Object            & MJD           &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)  &  $\eta_{\rm Edd}$  \\
                      &                  &                                      &                              & \\
    \hline
                      & $^{\dagger }$53498  &  9.49              &  47.22                  &  -0.378   \\
                      & 53498                      &    9.39            &                    &  $-$0.61   \\
 J1205+3422 & 58538                       &    9.78           &                      &   $-$1.76 \\  
                     & 58693                         &    9.38          &                   &  $-$1.26  \\                    
    \hline
                     & $^{\dagger }$54553    &  8.74            &  46.17   & $-$0.677  \\
                     & 54553                         &   8.84                 &             & $-$1.03  \\
J1638+2827  & $^{\ddagger }$55832  &    9.13                  & 45.98   & $-$1.21  \\      
                      & 55832                        &   8.80                  & 45.98   & $-$1.21  \\     
                      & 58583                        &   9.01                  & 46.50   & $-$0.69   \\
    \hline
                         & $^{\ddagger }$56189   & 8.73                  & 46.23  &  $-$1.24 \\
                         & 56189                         & 8.70                  & 46.23  &  $-$1.24 \\
J2228+2201     & 56960                          &  9.39               & 47.34  & $-$0.12  \\      
                         & 58693                         &  8.97               & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{The \civ\ virial mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars.
    The virial masses are calculated using the measured monochromatic luminosites and FWHM
    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
    We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}
